---
title: "Suplementary Materials: Maternal Judgements of Child Numeracy and Reading Ability Predict Gains in Academic Achievement and Interest"
output: 
  hrbrthemes::ipsum:
    toc: true
---

```{r include=FALSE, message=FALSE,warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE,warning=FALSE)
source(here::here("code","packages.R"))
source(here::here("code","custom_functions.R"))
library(DT)
library(hrbrthemes)
library(drake)
library(MplusAutomation)
update_geom_font_defaults(font_rc)
mplus_sum <- readModels("./mplus/")
```

Domains are Math = Numeracy domain and Read = Reading domain.
<br><br>

# Model Fits

```{r}
#loadd(mplus_sum)
mplus_sum %>%
   map(`[[`, "summaries") %>%
       map_df(as_tibble) %>% 
  # Note latent interaction means no fit statistics. Droping models
  filter(!str_detect(Title,"Polynomial")) %>%
  select(Title, ChiSqM_Mean, ChiSqM_DF,
         RMSEA_Mean,TLI_Mean, CFI_Mean) %>%
  set_names(c('Model', 'Chi-sq', 'DF', 'RMSEA', 'TLI','CFI')) %>%
  arrange(Model) %>%
  datatable(
    caption = "Table S1. Model Fit Statistics for Within and Between Models."
  )
```

*Notes.* RI-CLPM = Random Intercept Cross-lagged panel model (Within model). CLPM = Cross-lagged panel model (Between model). Lag 1 and 2 relates to autoregressive parameters.

<br><br>

# Assumption Checks

```{r, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(googlesheets4)
assump <- read_sheet("1qEJvz45Pm6HSDpRQArRQTCF6ecAGidcibhrje3M8iJI") %>%
  filter(`Model Type` == 'Cross-sectional') %>%
  select(-`Model Type`)
datatable(assump, filter = 'top', caption = 'Table S2. Assumption Checks')
```

<br><br>

# Gender by (Urban, Indigenous, SES, and LOTE) Interaction

```{r}
y = c(3,5,7)
d = c('math', 'read')
comb = crossing(d,y)
loadd(glue("bias_mod_svy_int_{comb$d}_{comb$y}"))

bind_rows(bias_mod_svy_int_math_3$result %>%
            mutate(Domain = "Math", Year = 3, .before = variable),
          bias_mod_svy_int_math_5$result %>%
            mutate(Domain = "Math", Year = 5, .before = variable),
          bias_mod_svy_int_math_7$result %>%
            mutate(Domain = "Math", Year = 7, .before = variable),
          bias_mod_svy_int_read_3$result %>%
            mutate(Domain = "Read", Year = 3, .before = variable),
          bias_mod_svy_int_read_5$result %>%
            mutate(Domain = "Read", Year = 5, .before = variable),
          bias_mod_svy_int_read_7$result %>%
            mutate(Domain = "Read", Year = 7, .before = variable)) %>%
  regex_left_join(variable_rename,c(variable = "variable_regex")) %>%
  relocate(new, .before = variable) %>%
  mutate(across(results:`upper)`, exp)) %>%
  select(-variable, -se, -missInfo,-variable_regex) %>%
  rename(Predictor = 3 ,`Odds-ratio` = 4,`-95% CI` = 5, `+95% CI` = 6) %>%
  datatable(filter = "top",
    caption = "Table S6. Gender Interaction Models."
  ) %>%
  formatRound(columns = 4:6, digits = 2)
  
```

<br><br>

# Gender by Urban

```{r}
loadd(bias_mod_urban_math_3,bias_mod_urban_read_7)

bind_rows(bias_mod_urban_math_3$result %>%
            mutate(Domain = "Math", Year = 3, .before = variable),
          bias_mod_urban_read_7$result %>%
            mutate(Domain = "Read", Year = 7, .before = variable)) %>%
  regex_left_join(variable_rename,c(variable = "variable_regex")) %>%
  relocate(new, .before = variable) %>%
  select(-variable, -se, -missInfo,-variable_regex) %>%
  mutate(across(results:`upper)`, exp)) %>%
  rename(Predictor = 3 ,`Odds-ratio` = 4,`-95% CI` = 5, `+95% CI` = 6) %>%
  datatable(filter = "top",
    caption = "Table S3. Gender by Urban Interaction Models."
  ) %>%
  formatRound(columns = 4:6, digits = 2)
```
<br><br>

# Moderation by Gender

```{r}
cro <- expand.grid(list(a = c('Interest', 'Achievement', 'Maternal Judgement'),
                  b = c('Interest', 'Achievement', 'Maternal Judgement'))
)

cro <- bind_rows(cro,cro, .id = "domain") %>%
  mutate(domain = case_when(
    domain == 1 ~ 'Math',
    domain == 2 ~ 'Read'
  ))

mplus_sum %>%
  purrr::keep(names(.)== 'Math_RI.CLPM_gender_moderation.out' |names(.)== 'Read_RI.CLPM_gender_moderation.out') %>%
   map(`[[`, "parameters") %>%
  map(`[[`, "ci.unstandardized") %>%
       map_df(as_tibble) %>% 
  # Note latent interaction means no fit statistics. Droping models
  filter(str_detect(param, "CONT") ) %>%
  select(`Estimated Difference` = est, `-95% CI` = low2.5, `+95% CI` = up2.5) %>%
  mutate(Domain = cro$domain, Contrast =  glue::glue("{cro$b} on {cro$a}"),.before = `Estimated Difference`) %>%
  datatable(filter = "top",
    caption = "Table S4. Gender Moderation of RI-CLPM (Unstandardized estimates)."
  ) %>%
  formatRound(columns = 4:6, digits = 2)
```

*Notes.* The estimates are on an unstandardized metric because slightly different variances across lags or groups make comparison on a standardized metric difficult.
<br><br>

# Polynomials

```{r}
cro <- data.frame(a = c('Interest Year 5', 'Achievement Year 5',
                        'Interest Year 7', 'Achievement Year 7'),
                  b = rep(c('Judgement Year 3', 'Judgement Year 5'), each = 2)
)

cro <- bind_rows(cro,cro, .id = "domain") %>%
  mutate(domain = case_when(
    domain == 1 ~ 'Math',
    domain == 2 ~ 'Reading'
  ))

mplus_sum %>%
  purrr::keep(names(.)== 'Math_RI.CLPM.polynomial.3.5.out' |
              names(.)== 'Math_RI.CLPM.polynomial.5.7.out' | 
              names(.)== 'Read_RI.CLPM.polynomial.3.5.out' |
              names(.)== 'Read_RI.CLPM.polynomial.5.7.out') %>%
   map(`[[`, "parameters") %>%
  map(`[[`, "ci.stdyx.standardized") %>%
       map_df(as_tibble) %>% 
  filter(str_detect(param, '_2$')) %>%
  select(`Estimated Difference` = est, `-95% CI` = low2.5, `+95% CI` = up2.5) %>%
  mutate(Domain = cro$domain, Contrast =  glue::glue("{cro$a} on {cro$b}"),.before = `Estimated Difference`) %>%
  datatable(filter = "top",
    caption = "Table S5. Maternal Judgement Polynomails"
  ) %>%
  formatRound(columns = 4:6, digits = 2)
```
<br><br>

# Mediation

```{r}
math_med <- my_extract_indirect_2("mplus/Math_RI-CLPM.out",type = 'Math')
read_med <- my_extract_indirect_2("mplus/Read_RI-CLPM.out",type = 'Read')

bind_rows(math_med, read_med,.id = 'Domain') %>%
  select(-Effect) %>%
  mutate(Domain = case_when(
    Domain == 1 ~ 'Math',
    Domain == 2 ~ 'Reading'
  )) %>%
  datatable(filter = "top",
    caption = "Table S6. Maternal Judgements Predicting Achievement via Interest"
  ) %>%
  formatRound(columns = 4:6, digits = 2)
```
